Data Exploration

### 2018-11-14 src/data_exploration.Rmd
histogram addition + start of boxplots

>>>>

XXX SAM - YOU WANT TO THINK ABOUT DOING THIS BY DEPTH RATHER THAN ALL DEPTHS)

```{r}
unique_depths <- unique(presence$depthlayerno)
unique_depthdordered <- sort(unique_depths) #just puts the list in oder with no NA
length(unique_depthdordered)
```
ouch - 40 layers... a job for a boxplot probably

```{r}

```

# frequency plots of env. corr

just do surface layers for now

temperature
```{r}
hist(presence$temp_surface, main = "Temp at Surface", xlab = "Kelvin")
dev.copy(png, "../output/env/simple_plots/temperature_surface_histogram.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

# simple boxplots of env. corr

Same as above but with boxplots (may provide some more useful info)

XXX SAM YOU WANT TO PUT THE TWO LAYERS ON THE ONE PLOT - NOT TWO SIDE BY SIDE

temperature
```{r}
par(mfrow=c(1,2))
boxplot(presence$temp_depth, main = "Temp at Depth (Various)", ylab = "Kelvin")
boxplot(presence$temp_surface, main = "Temp at Surface", ylab = "Kelvin")
dev.copy(png, "../output/env/simple_plots/temperature_boxplot.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```
